Template Title

### 2024-06-28 Extract data.Rmd
edits

```{r}
QGShell <- read_csv(file=here("data","QG1-7246-1-A30Centre_analyzed_data.csv"), col_names = c("x", "y", "z", "mg_ca", "std", "relstd")) %>%
  mutate(sampleID = "QG1-7246-1") %>%
  filter(relstd<0.1,
         x>1.3) %>% 
  mutate(x=round(x,2)) %>% 
  group_by(y) %>% 
  mutate(mg_ca=mean(mg_ca),
         std=mean(std),
         n=n()) %>% 
  ungroup() %>% 
  filter(n>1) %>% 
  select(sampleID,everything(),-n) %>% 
  arrange(y) %>% 
  mutate(dist=row_number()*0.03)

QGShell %>% 
  ggplot()+
  aes(y,mg_ca)+
  geom_line()

@@

```{r}

write_csv(bind_rows(MgCa,QGShell),file=here("data","MgCa.csv"))

>>>>

```{r}
MgCa <- read_csv(here("data","MgCa.csv"))

NM_1016_1 <- MgCa %>% 
  filter(sampleID=="NM-1016-1") #%>% 
  # select(-sampleID,-dist)

NM_1016_1 %>% 
  filter(std<0.01) %>% 
  ggplot()+
  aes(x=dist,y=mg_ca)+
  geom_path()

# write_csv(QG1_7246,file = here("data","export","QG1_7246.csv"))

@@
